Supporting Information for: \\ Large scale risks from agricultural pesticides in small streams

### 2017-06-04 supplement/Supplemental_Materials.tex
comments from rs
first draft

%% -------------------------------------------------------------------------
\title{Supplemental Materials for: \\ Large scale risks from pesticides in small streams}
\author{Eduard Szöcs%
  \thanks{Corresponding author, Email: \texttt{szoecs@uni-landau.de}}}
\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Germany}

@@

\author[1]{Ralf B. Schäfer}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{data_cleaning}
	\caption[Overview on data cleaning steps.]{Overview on data cleaning steps. After cleaning, data have been stored in a relational spatial PostgreSQL database.}
	\label{fig:data_cleaning}
\end{figure}

%% -------------------------------------------------------------------------
\chapter{Overview on compiled data}
% Overview samples
% table generated in do_overview.R
\input{phchoverview}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{ezgagrirac}
	\caption[Raw data used for the model in Eqn. 2 and Fig. 3 of the main article.]{Raw data used for the model in equation 2 and Figure 3 of the main article. Color codes the number of RAC exceedances (on a log-scale). Grey points denote sites without any exceedance.}
	\label{fig:ezgagrirac}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{coefs}
	\caption[Graphical representation of coefficients from table \ref{tab:var_model_coef}.]{Graphical representation of coefficients from table \ref{tab:var_model_coef}. Top row: Effect of precipitation at the day before sampling and at day of sampling. Bottom row: estimates for the four quarters of the year. Each dot represents one compound (in the order described in table \ref{tab:var_model}). Coefficients where the CI encompasses zero are shown in gray colour. Coefficients are shown on the link scale (log for $\mu$ and logit for $\nu$).}
	\label{fig:coefs}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{width_size}
	\caption[Relationship between catchment size and stream width.]{Relationship between catchment size and stream width. A power function has been fitted to each dataset separately (colored dashed lines) and the combined dataset (black line and equation). The gray rectangle marks the estimated catchment size for a width of 1 m (=7 km\textsuperscript{2}). Data has been compiled from three different sources (\citet{Fern2015}, \citet{Voss2015} and the federal state of Thuringia)}
	\label{fig:size_width}
\end{figure}

\bibliographystyle{apalike}      % basic style, author-year citations
\bibliography{references}

>>>>

%% -------------------------------------------------------------------------
\title{Supporting Information for: \\ Large scale risks from agricultural pesticides in small streams}
\author{Eduard Szöcs}
\affil[1]{Institute for Environmental Sciences, University of Koblenz-Landau, Germany}

@@

\author[1]{Ralf B. Schäfer   
\thanks{Corresponding author, Email: \texttt{schaefer-ralf@uni-landau.de}}}

\date{}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{data_cleaning}
	\caption[Overview of data cleaning steps.]{Overview of data cleaning steps. After cleaning, data have been stored in a relational spatial PostgreSQL database.}
	\label{fig:data_cleaning}
\end{figure}

%% -------------------------------------------------------------------------
\chapter{Overview of compiled data}
% Overview samples
% table generated in do_overview.R
\input{phchoverview}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{ezgagrirac}
	\caption[Raw data used for the model in Eqn. 2 and Fig. 3 of the main article.]{Raw data used for the model in equation 2 and Figure 3 of the main article. Color codes the number of RAC exceedances (on a log-scale). Grey dots denote sites without any exceedance.}
	\label{fig:ezgagrirac}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{coefs}
	\caption[Graphical representation of coefficients from table \ref{tab:var_model_coef}.]{Graphical representation of coefficients from table \ref{tab:var_model_coef}. Top row: Effect of precipitation at the day before sampling and at day of sampling. Bottom row: estimates for the four quarters of the year. Each dot represents one compound (in the order described in table \ref{tab:var_model}). Coefficients where the CI encompasses zero are shown in grey colour. Coefficients are shown on the link scale (log for $\mu$ and logit for $\nu$).}
	\label{fig:coefs}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{width_size}
	\caption[Relationship between catchment size and stream width.]{Relationship between catchment size and stream width. A power function was fitted to each dataset separately (colored dashed lines) and the combined dataset (black line and equation). The grey rectangle marks the estimated catchment size for a width of 1 m (=7 km\textsuperscript{2}). Data was compiled from three different sources: \citet{Fern2015}, \citet{Voss2015} and the federal state of Thuringia.}
	\label{fig:size_width}
\end{figure}

\bibliographystyle{spbasic}      % basic style, author-year citations
\bibliography{references}
